AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-18 Latex/Paper/main.tex
Final final

In closing we have presented an algorithm in this paper that gives satisfying results when trying to exact the exact time points at which base drum hits happen in a drum track.
It can easily be extended to other percussive instruments and maybe even other melodic instruments.
The accuracy and precision could be improved in future work by the methods mentioned.

@@

%\end{document}

% DELETE EVERYTHING FROM HERE IN THE END
% DELETE EVERYTHING FROM HERE IN THE END
% DELETE EVERYTHING FROM HERE IN THE END

\vfill\pagebreak

\section{common flaws}
all cited papers should appear in bibliography
vice versa: all references should be mentioned in the paper
each reference should contain:
names of authors
title of the paper or book
conference paper: name of conf. incl. year and location
journal paper: name of journal incl. volume, year and pages
book: publisher, potentially editor
all figures and tables must be referenced in the paper
equations:
all mathematical symbols must be explained
symbols should be used consistently and unambiguously
abbreviations (STFT, DFT, etc.) should be introduced
”The short-time Fourier transform (STFT) is given by (. . .)
We compute the STFT of the signal, (. . .)”

\section{Evaluation}

form (structure, language, form of references)
content (introduction, literature review, algorithm and
evaluation description, figures, comprehensibility, correctness)
evaluation (dataset, metrics, discussion)

>>>>

In closing we have presented an algorithm that gives satisfying results when trying to exact the time points at which base drum hits happen in a drum track.
It can easily be extended to other percussive instruments and maybe even other melodic instruments.
The accuracy and precision could be improved in future work by the methods mentioned.

@@
